Quantifying the ease of viral escape from broad and narrow antibodies to influenza virus hemagglutinin

### 2017-10-07 paper/manuscript.tex
analysis notebook thru logo plots

\subsection*{A method to quantify the ease of escape.}
\comment{Jesse writes a draft of this section.}
\begin{figure}
\centerline{\includegraphics[width=0.8\textwidth]{figs/fracsurvive_example/frac_survive_example_plot.pdf}}
\caption{\label{fig:fracsurvive_example}
CAPTION}
\end{figure}

\subsection*{Broad and narrow antibodies that neutralize influenza virus hemagglutinin}
\comment{Juhye writes a draft of this section.}
\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/antibody_summary_fig/antibody_summary_fig.pdf}}
\caption{\label{fig:antibody_summary}
CAPTION
\comment{Can you make the following changes:
(1) Add H17-L10 and H17-L7. These could just be in different shades of red since they are all narrow antibodies like H17-L19. (2) Make the structure slightly larger relative to the tree. (3) Increase the line widths on the tree and the font sizes everywhere. (4) Move the color-based label to the left side of the tree so it falls between the two panels, since it is really labeling both. (5) Make the tree branches all black. Since color is already being used to represent the different antibodies, I think it is confusing to also use it to distinguish Group 1 and Group 2.}}
\end{figure}

@@

>>>>

\subsection*{A method to quantify the ease of escape.}
\comment{Jesse writes a draft of this section.}
\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/fracsurvive_example/fracsurvive_fig.pdf}}
\caption{\label{fig:fracsurvive_example}
CAPTION}
\end{figure}

\subsection*{Broad and narrow antibodies that neutralize influenza virus hemagglutinin}
\comment{Juhye writes a draft of this section.}
\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/antibody_summary_fig/Ab_summary.pdf}}
\caption{\label{fig:antibody_summary}
CAPTION
\comment{Can you make the following changes:
(1) Add H17-L10 and H17-L7. These could just be in different shades of red since they are all narrow antibodies like H17-L19. (2) Make the structure slightly larger relative to the tree. (3) Increase the line widths on the tree and the font sizes everywhere. (4) Move the color-based label to the left side of the tree so it falls between the two panels, since it is really labeling both. (5) Make the tree branches all black. Since color is already being used to represent the different antibodies, I think it is confusing to also use it to distinguish Group 1 and Group 2.}}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{../analysis_code/results/fracsurvive/summary_medianavgfracsurvive.pdf}}
\caption{
CAPTION
}
\end{figure}
